\section{Project outcomes}

\subsection{Concrete outcomes}
Describe the artifacts you've produced, if possible by linking to repo commits.
For those who choose to work on an open source project, please put here the
\textbf{URL to your final pull request}.

Those that have chosen to present a paper can include a link to the slides.

\subsection{Learning outcomes}

What was the most important thing all the members have learned while
developing this part of the project, what questions remained unanswered,
how you will use what you've learned in your everyday life?
Please also indicate which tools you learned to use.

Examples:

\begin{itemize}
  \item Foo learned to write multithreaded applications, he's probably going to
        create his own startup with what she has learned. She also learned how to
        debug with gdb.
  \item Bar learned how to interact with the open source community, politely
        answering to code reviews and issuing pull requests through Git.
\end{itemize}

\subsection{Existing knowledge}
What courses you have followed (not only AOS) did help you in doing this project
and why? Do you have any suggestions on improving the AOS course with topics
that would have made it easier for you?

\subsection{Problems encountered}
What were the most important problems and issues you encountered? Did you ever
encountered them before?

\begin{itemize}
  \item Foo encountered a problem with some critical sections. He ended up
        rewriting existing lock implementation.
\end{itemize}